---
title: "HW1"
format: pdf
author: Carrie
---

```{r}
library(Hmisc)
library(vtable)
library(ggplot2)
```

```{r}
df = read.csv("titanic.csv")
```

#####  The Titanic dataset contains the details of 891 passengers on board with 12 variables, which are as follows 
| 1.PassengerId : 1 - 891.
| 2.Survived : "0" respresens not survived,"1" represents survived.   
| 3.Pclass :  1 - 3  
| 4.Name : It's characters.
| 5.Sex : "female"、"male"
| 6.Age : 0.42 - 80
| 7.SibSp : 0 - 8
| 8.Parch : 0 - 6
| 9.Ticket :It's characters.
| 10.Fare : 0 - 512.33
| 11.Cabin :It's characters.
| 12.Embarked : "S","C","Q"

##### From the table ,we can know that:

* There are 177 missing in variable "Age" and lots of missing value in variable "Cabin".
* There are some odd value, such as A/5 21171,PC 17599 that needs to be well-defined in the future.
```{r}
describe(df)
```

```{r}
st(df)
```

##### From the histgram ,we can know that most poeple's age is between 20-40. 

```{r}
ggplot(df,aes(x = Age)) + geom_histogram()
```

##### And from the barchart, we can know that survuved people is less than the not-survuved ones.
```{r}
ggplot(data = df) + geom_bar(mapping = aes(x = Survived))
```